---
title       : Fantasy Football Rankings and Tiers
subtitle    : version 0.01
author      : hcam
job         : Rn00b
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
    user: hcam
    repo: slidifyFF16
    
---

## Fantasy Football Rankings and Tiers

Welcome to the 2016 Fantasy Football Season. 

Data is provided from borischen.co and fantasypros.com.


--- .class #id 

## Purpose

In order to help with your draft this season.  We pulled the rankings and tiers from borischen.co and presented it in two tabs ("Top 200" and "By Position").  Feel free to use this to dominate your draft, and set your team up for sucess this season.  

---

## Prepping data

```{r, echo = T, message = F}
require(dplyr)
dataurl <- "https://s3-us-west-1.amazonaws.com/fftiers/out/current/weekly-ALL.csv"
ffdata <- read.csv(dataurl, stringsAsFactors = FALSE)
ffdata$Pos <- gsub('[0-9]+', '', ffdata$Position) #creates new column for Position
print(head(ffdata))
```

---

## Using dplyr package to filter data.

```{r, echo = T, message = F}
head(filter(ffdata, Pos == "WR"))
```
# Good luck to all in your drafts this season! More updates to come!



